---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---
```{r}
library(curl)
library(nhlapi)
library(ggplot2)
library(reactable)
library(tidyverse)
```




This is a function to check and see if the Red Wings played the previous day.

could be modified to take a teamId as a parameter to get any team.

```{r}
did_wings_play = function(){

  yday = Sys.Date() - 1

  #games_today = nhlapi::nhl_schedule_today()
  games_today = nhlapi::nhl_schedule_date_range(yday, yday)[[1]]

  games = games_today$dates$games[[1]]

    for (i in 1:nrow(games)){
  
    homeid = games$teams.home.team.id[i]
    #print(homeid)
    awayid = games$teams.away.team.id[i]
    #print(awayid)
    if ( homeid == 17){
      wings_game_id = games$gamePk[i]
    } else if (awayid == 17) {
      wings_game_id = games$gamePk[i]
    }
  }
  return(wings_game_id)
}

game_id = did_wings_play()
```

This function returns a dataframe with all sorts of team info from the current season, as well as another data frame that contains the current season stats and ranking like goals, wins, pp%, etc. "season" and "season_ranks".

```{r}
season_stats = function() {
  
  wings_season = nhlapi::nhl_teams_stats(17, 2022)
  
  stats = wings_season$teamStats[[1]]
  
  return(stats)
  
}

season = season_stats()[[1]]
season_ranks = season[[1]]

```


This function creates a data frame called "feed" that contains all info about a
single game.

```{r}
### single game live event stat
live_feed = function() {
  
  game_events = nhlapi::nhl_games_feed(game_id)[[1]]
  plays = game_events$liveData
  
  return(game_events)
}

feed = live_feed()
#feed
```

```{r}

game_events = nhlapi::nhl_games_feed(game_id)

plays = as.data.frame(game_events[[1]]$liveData$plays$allPlays)
plays

players = plays$players
#players

shots = plays[plays$result.event == "Shot" | plays$result.event == "Goal",]
shots

goals = plays[plays$result.event == "Goal",]
goals
```

```{r}
#attempting to plot shots

plot(shots$coordinates.x, shots$coordinates.y, axes = TRUE,
     xlim = c(-100, 100),
     ylim = c(-42.5, 42.5))
abline(v=-25, col='blue')
abline(v=25, col='blue')
abline(v=0, col='red')
abline(v=-89, col='red')
abline(v=89, col='red')

plot(goals$coordinates.x, goals$coordinates.y, axes = TRUE, col="red",
     xlim = c(-100, 100),
     ylim = c(-42.5, 42.5))
abline(v=-25, col='blue')
abline(v=25, col='blue')
abline(v=0, col='red')
abline(v=-89, col='red')
abline(v=89, col='red')
```



```{r}
scrape_shots = function(ids) {
  game_events = nhlapi::nhl_games_feed(ids)
  plays = as.data.frame(game_events[[1]]$liveData$plays$allPlays)
  shots = plays[plays$result.event == "Shot" | plays$result.event == "Goal",]
  return(shots)
}
```


```{r}
# There are 82*32 = 2624 games in a season
# for many seasons there are less games though, only 32 teams since 2021

# 2018 season type 1, games go up to 111, I think type 1 is preseason
# for 2018 type 2, we see 1272 games, not sure if this is accurate though.

ids = c(2018020001:2018022625)

shots2018 = data.frame()

for(gameid in ids) {
  print(gameid)
  
  shots2018 = bind_rows(shots2018, scrape_shots(gameid))
}

shots_clean = shots2018 %>% 
  filter(is.na(result.emptyNet) | result.emptyNet == FALSE) %>% 
  filter(is.na(result.strength.code) | result.strength.code == "EVEN") 

# tested how many games are actually available, for 2021 it was 1312, not sure why though
#shots2018 = scrape_shots(2021021312)
pwd = "/Users/aaronweiss/Documents/Class_Files/1. Math 560 - Optimization/shots.csv"

shots_clean <- apply(shots_clean,2,as.character)

library(dplyr)
write.csv(shots_clean, pwd, row.names = F)

```


```{r}
games = nhl_schedule_seasons(seasons = 20212022)

gameids = games[[1]]$dates$game
```







